\LaTeXe\ guide for the Journal of Functional Programming

### 2019-04-24 papers/jfp/3-abstractions.tex
Tweaks to S3.8

\noindent
The \hs{Tasks} abstraction allows us to express pure functions in a way that
is convenient for their memoization and incremental recomputation
(see~\S\ref{sec-related-memo} for a discussion on memoization). If we
furthermore need to share computation results via a cloud cache, we can use
\hs{Tasks}~\hs{(MonadState}~\hs{s)} that will
play an important role in~\S\ref{sec-implementations}. Intuitively, by making
a shared state of type \hs{s} available to a task, we give it the abilities to
lookup and store computation results in a cache by using the \hs{MonadState}
methods \hs{get} and \hs{set}. For example, below we implement a cloud version
of the Ackermann task that uses a \hs{Cache} of type
\hs{Map}~\hs{(Integer,}~\hs{Integer)}~\hs{Integer} for sharing results of known
Ackermann values.

@@

\noindent
The main case ($m>0 \wedge n>0$) starts by looking up the pair of indices
\hs{(}\hs{m,}~\hs{n)} in the \hs{cache}. If the cache has \hs{Nothing}, we
calculate the resulting \hs{value} as before and \hs{modify} the cache
accordingly; otherwise, if we have a cache hit, we return the obtained value
immediately, skipping the actual calculation. We will use this technique in our
models of cloud build systems in~\S\ref{sec-implementations}.

>>>>

\noindent
The \hs{Tasks} abstraction allows us to express pure functions in a way that
is convenient for their memoization and incremental recomputation
(see~\S\ref{sec-related-memo} for a discussion on memoization). If we
furthermore need to share computation results via a cloud cache, we can use
\hs{Tasks}~\hs{(MonadState}~\hs{s)} that will
play an important role in~\S\ref{sec-implementations}. Intuitively, by making
a shared state of type \hs{s} available to a task, we give it the abilities to
lookup and update cached computation results using the \hs{MonadState} methods
\hs{get} and \hs{modify}. For example, below we implement a cloud version of the
Ackermann task that uses a \hs{Cache} of type
\hs{Map}~\hs{(Integer,}~\hs{Integer)}~\hs{Integer} for sharing results of known
Ackermann values.

@@

\noindent
The main case ($m>0 \wedge n>0$) starts by looking up the pair of indices
\hs{(}\hs{m,}~\hs{n)} in the \hs{cache}. If the cache has \hs{Nothing}, we
calculate the resulting \hs{value} as before and \hs{modify} the cache
accordingly; otherwise, if we have a cache hit, we return the obtained value
immediately, skipping the actual calculation and thus potentially saving a large
amount of work. Indeed you do not want to recompute $A(4,2)=2^{65536}-3$
unnecessarily; all of its 19,729 decimal digits have already been helpfully
computed, e.g. see~\cite{ackermann42}. We will use this technique in our models
of cloud build systems in~\S\ref{sec-implementations}.
